---
title: "Assignment 1"
author: "Philipp Epstein"
date: "10/14/2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=35),tidy=TRUE)
```

# Introduction

This report is written for the 1st assignment of the Financial Trading Systems course 2018 at the Bond University. During the first weeks we learned how to use the Blotter Framework in R to implement a trading strategy, backtest the strategy on a set of instruments (stock, futures, etc.) and visualize meaningful results which give insights about the strategy. Moreover, we learned how to compare the strategy to another alternative (e.g. a buy and hold strategy). The trading idea, implementation and analysis and results are summarized in the following report.

# Trading Idea
## Smash Day by Larry Williams
The trading idea which is used for this report is based on the Smash Day strategy introduced by Larry Williams in his book "Long Term Secrets to short term trading" 2012. 
The basic theoretical foundation is set by the concept of autocorrelation. There are two autocorrelation principles which can be empirically observed. The positive autocorrelation which describes the fact that if we observe an upward movement it is more likely to observe an upward movement in the future. The same is valid for a negative trend. However, the negative autocorreleation can be observed on short term time periods. We can expect a price to bounce up again after a sharp down movement and vice versa. 
Larry William's Smash Day pattern is based on the observation of this autocorrelation behaviour. 
A Smash Day pattern is initialized when we observe a close which is lower than the previous day's low. This looks like a breakout to the downside. If the very next day the price moves opposite the Smash Day and trades above the high of the Smash Day this is according to Williams a buy signal. 
Williams explains this buy signal with a feeling of hurt felt by the public as a result of an unfulfilled breakout. The public would want to get back on track and the price responds with a reversal. 
The exact opposite is true for a Sell setup. The Smash Day is set up when we observe a close above the previous day's high. The sell signal is initiated when the price reverses immidiately the next day and falls below the smash day's low.

## Own variation of the Smash Day trading strategy

In addition to the Smash Day pattern, I have incorporated another rule for the buy signal and 2 additional components for the sell signal.
I want to make sure that I only enter long when we are observing a longlasting upward trend. In order to do this buy orders are only performed when the current price is above the exponential moving average of the last 200 days.
After that the Smash Day pattern is checked.
For the sell I incorporated two "harder" conditions before checking whether we observe a Smash Day (sell). The first is that a maximum holding period can be set in order to make sure that a position is not open for too long. The second sell case is when the price falls below the 200 day exponential moving average the position is liquidated. If both is not the case a check for the smash day pattern is performed. If we observe it, we sell the current position.

These variations are incorporated to reduce the risk of falling prices. 

# Implementation of the trading idea

## Part A: Initialization

### Step 1: General Setup
The environment has to be cleared in order to ensure a reproducable setup. Moreover, the blotter library and the INF361Course library are loaded.

```{r message=FALSE}
# Clear Environment
rm(list=ls())

# Loading libraries
library(blotter)
library(INFT361Course)
```

### Step 2: Setting the Variables
The variables set in the next section can be adjusted to test the strategy with different parameters. The critical variables which should be adjusted to test the strategy are:
* daterange
* emaPeriod
* maxHoldingPeriod
* instrumentlist
* BuyHoldInstrument

```{r message=FALSE, results="hide"}
# Set values:
startCapital <- 1e+6
transactionCost <- -20
daterange <- '2000::2018' 
emaPeriod <- 400
maxHoldingPeriod <- 4

InstrumentDirectory <- "~/Desktop/R/DownloadedData/"
instrumentlist <- c("BMW.csv","DAI.csv", "DTE.csv", "FME.csv", "FRE.csv")
BuyHoldDirectory <- "~/Desktop/R/DownloadedData/"
BuyHoldInstrument <- "DAXEX.csv"

currency("EUR")
Sys.setenv(TZ="UTC") 
initdate <- '1999-12-31'
startdate <- '2000-01-01' 
enddate <- '2018-12-31' 
portfolioname <- "Smash Day" 
accountname <- portfolioname
```

### Step 3: Presetup for plotting graphs
Some setup for plotting the graphs in the visualization is performed here to ensure that the Theme is available later, when it is needed and used.

```{r message=FALSE, echo=TRUE}  
# Settings for graph
myTheme <- chart_theme()
myTheme$col$up.col <- 'lightblue'
myTheme$col$dn.col <- 'brown'
myTheme$col$dn.border <- 'lightgray'
myTheme$col$up.border <- 'lightgray'

# Concatenate string for EMA with input parameter
addEMAString <- paste("add_EMA(n=",emaPeriod,")",sep = "")

```


### Step 4: Initializing the portfolio
The portfolio takes the instrumentlist which includes all the stocks we defined in Step 2. 

```{r message=FALSE, results="hide"}
# Clear portfolio and Account
suppressWarnings(rm("account.Smash Day","portfolio.Smash Day",
                    "account.buyhold","portfolio.buyhold",
                    pos=.blotter))

# Initialize Portfolio and Account
initPortf(portfolioname,
          instrumentlist,
          initDate=initdate,
          currency="EUR")

initAcct(accountname,
         portfolios=portfolioname,
         initDate=initdate,
         initEq=startCapital,
         currency="EUR")
```


## Part B: Bar by bar processing
### Step 1: Go through the data bar by bar
In this step the bar by bar processing is implemented. Thus, a for loop is implemented to loop through the instrumentlist. For each instrument in the list the data is loaded and the exponential moving average is added to the data. Furthermore, another for loop is used to loop through the dates bar by bar. In this step the defined strategy is applied.

```{r message=FALSE, results="hide"}
for (instrument in instrumentlist) {
    LoadCourseFile(InstrumentDirectory, instrument, debugme = TRUE, dates = daterange)
    
    # Initialize the instrument
    stock(instrument, currency = "EUR")
    
    # Load the XTS file
    symbol <- get(instrument)
    
    # Calculate the Exponential Moving Average
    ema <- EMA(symbol$Close, n=emaPeriod)
    
    # Merge the xts file with the Exponential Moving Average
    symbol <- merge(symbol,ema)
    assign(instrument,symbol)
  # Starting to go bar by bar through using a "for loop"
  for (i in (emaPeriod + 1):(nrow(symbol) - 1)) {
    # Dates
    CurrentDate <- time(symbol[i])
    TomorrowDate <- time(symbol[i + 1])
    
    # Today's variables
    CloseToday <- as.numeric(symbol[i, "Close"])
    EMA_today <- as.numeric(symbol[i, "EMA"])
    LowToday <- as.numeric(symbol[i, "Low"])
    HighToday <- as.numeric(symbol[i, "High"])
    
    # Yesterday's variables
    LowYesterday <- as.numeric(symbol[i - 1, "Low"])
    HighYesterday <- as.numeric(symbol[i - 1, "High"])
    
    # Tomorrow's variables
    OpenTomorrow <- as.numeric(symbol[i + 1, "Open"])
    LowTomorrow <- as.numeric(symbol[i + 1, "Low"])
    HighTomorrow <- as.numeric(symbol[i + 1, "High"])
    
    # Config
    Equity <- getEndEq(accountname, CurrentDate)
    Position <-
      getPosQty(portfolioname, Symbol = instrument, Date = CurrentDate)
    
    # Check whether we have a position
    if (Position == 0) {
      # Start checking BUY rules
      
      # Check whether we have a Smash Day (Buy).
      # Smash Day (Buy) is when Todays Close is below Yesterdays Low.
      if (CloseToday < LowYesterday) {
        # Smash Day (Buy)
        
        #Check whether todays close is above today's EMA
        if (CloseToday > EMA_today) {
          
          # BUY RULE: If today was a smash day place a STOP BUY order 
          # at todays high price for the next day. 
          # (Buy tomorrow for 'price >= todays high')
          
          ######
          # Simulate STOP BUY order:
          ######
          
          # Option 1 to check: Check whether the open price tomorrow 
          # is above today's high and add the transaction tomorrow at
          # tomorrow's open price.
          
          # Option 2 to check: Check whether today's high was lower 
          # than tomorrows high and add the transaction tomorrow 
          # at today's high price 
          
          # Check Option 1
          if (OpenTomorrow > HighToday) {
            # Don't trade at the day before the last day
            if (CurrentDate != time(symbol[nrow(symbol) - 1])) {
              # Calculate the buy quantity
              BuyQuantity <- as.numeric(trunc(Equity / OpenTomorrow))
              # Add transaction
              addTxn(
                portfolioname,
                Symbol = instrument,
                TxnDate = TomorrowDate ,
                TxnPrice = OpenTomorrow,
                TxnQty = BuyQuantity,
                TxnFees = transactionCost
              )
              # Store the bar at which we placed the transaction
              BuyBar <- i
            }
            
          } else {
            # Check Option 2
            if (HighToday < HighTomorrow) {
              # Don't trade at the day before the last day
              if (CurrentDate != time(symbol[nrow(symbol) - 1])) {
                # Calculate the buy quantity
                BuyQuantity <- as.numeric(trunc(Equity / HighToday))
                # Add transaction
                addTxn(
                  portfolioname,
                  Symbol = instrument,
                  TxnDate = TomorrowDate ,
                  TxnPrice = HighToday,
                  TxnQty = BuyQuantity,
                  TxnFees = transactionCost
                )
                # Store the bar at which we placed the transaction
                BuyBar <- i
              }
            }
          }
        }
      }
    } else {
      # We already have a position
      
      # Check the sell rules in the following order and sell at the 
      # first condition which is satisfied.
      
      #####
      # SELL rules:
      #####
      
      # Rule 1: Sell if we hold the position longer than the specified 
      # maximum holding period
      
      # Rule 2: Sell at tomorrow's opening price if the close price 
      # today falls below the EMA
      
      # Rule 3: Sell if we meet the Smash Day (Sell) requirements. 
      # Today's close must be higher than yesterday's high
      
      # Rule 4: If no sell rule can be applied and we reach the 
      # second last day. Sell at the last day.
      
      # Check Rule 1:
      if ((i - BuyBar) > maxHoldingPeriod) {
        # Place the sell transaction at todays close price
        addTxn(
          portfolioname,
          Symbol = instrument,
          TxnDate = CurrentDate,
          TxnPrice = as.numeric(symbol[i, "Close"]),
          TxnQty = -Position,
          TxnFees = transactionCost
        )
        
      } else {
        # Check Rule 2:
        if (as.numeric(symbol[i, "Close"]) < EMA_today) {
          # Place the sell transaction at tomorrow's open price
          addTxn(
            portfolioname,
            Symbol = instrument,
            TxnDate = time(symbol[i + 1]),
            TxnPrice = OpenTomorrow,
            TxnQty = -Position,
            TxnFees = transactionCost
          )
          
        } else {
          # Check Rule 3:
          
          # Sell Rule 3: If today is a Smash Day (Sell) place an order tomorrow at todays 
          # low price.
          
          # Simulate this behaviour:
          
          # Option 1 to check: Check whether the open price tomorrow is below today's 
          # low and add the transaction tomorrow at tomorrow's open price.
          
          # Option 2 to check: Check whether today's low was larger than tomorrow's 
          # low and add the transaction tomorrow at today's low price.
          
          # Check for Smash Day (Sell)
          if (CloseToday > HighYesterday) {
            # Check for Option 1
            if (OpenTomorrow < LowToday) {
              # Add Sell transaction tomorrow at tomorrow's open price
              addTxn(
                portfolioname,
                Symbol = instrument,
                TxnDate = time(symbol[i + 1]),
                TxnPrice = OpenTomorrow,
                TxnQty = -Position,
                TxnFees = transactionCost
              )
              
            } else {
              # Check for Option 2
              if (LowToday > LowTomorrow) {
                # Add Sell transaction tomorrow at today's low price
                addTxn(
                  portfolioname,
                  Symbol = instrument,
                  TxnDate = time(symbol[i + 1]),
                  TxnPrice = LowToday,
                  TxnQty = -Position,
                  TxnFees = transactionCost
                )
              }
            }
          } else {
            # Check Rule 4
            if (i == nrow(symbol) - 1) {
              # Add Sell transaction for the last day at the close price
              addTxn(
                portfolioname,
                Symbol = instrument,
                TxnDate = time(symbol[i + 1]),
                TxnPrice = as.numeric(symbol[i, "Close"]),
                TxnQty = -Position,
                TxnFees = transactionCost
              )
            }
          }
        }
      }
    }
    
    updatePortf(portfolioname, Symbols = instrument, Dates = CurrentDate)
    updateAcct(accountname, Dates = CurrentDate)
    updateEndEq(accountname, CurrentDate)
    
  } # End Bar-by-bar processing
} # End for loop for multiple instruments
```

### Step 2: System Check
In order to make sure that the system works as designed the plots of some choosen transactions are printed in the following. The plots for the first, third and the 5th last trasnaction are plotted for every instrument in the instrumentlist. The plots can be checked manually and by this it can be ensured that the transactions were performed as expected.

```{r echo=TRUE, message=FALSE, warning=FALSE, results="hide"}
# Loop through all instruments in the instrumentlist
for (instrument in instrumentlist){
  rm(daterange_check)
  daterange_check <- c()
  transactionsInstrument <- getTxns(Portfolio=portfolioname,Symbol=instrument)
  
  # Create a list of transactions to check 
  for (i in 
       c(2,6, (nrow(transactionsInstrument)-7),(nrow(transactionsInstrument)-5))) {
    from <- as.Date(index(transactionsInstrument[i,1]))-7
    to <- as.Date(index(transactionsInstrument[i+1,1]))+7
    daterange_check <- c(daterange_check, paste(from, "::", to, sep = ""))
  }
  # Plot the transactions and check them manually
  for (daterange_check_i in daterange_check){
    print(chart.Posn(portfolioname,
                     Symbol=instrument,
                     type='candlesticks',
                     theme=myTheme,
                     subset=daterange_check_i,
                     TA=addEMAString))
  }
}
```

## Part C: Analysis and Reporting

### Step 1: Visualize original data
Plot of the instrument with the EMA line which indicates the general trend of the stock exponentially smoothed for the last 200 days. Moreover, the tradevolume is added below the graph. This plots can be used to get a first impression of the long term trend of the instrument and to see which general behaviour of the price can be observed 

```{r message=FALSE}
for (instrument in instrumentlist){
  chart <- get(instrument)
  print(chart_Series(x=chart,name=instrument,
                     theme=myTheme, 
                     subset=daterange,
                     TA="add_TA((chart$EMA), on=1,type='l',col='blue')"))
}
```

### Step 2: All transactions performed by the trading system
The following table can be used to get a better overview of the transactions performed and the exact details like the quantity, price and value per transaction.
```{r message=FALSE}
for (instrument in instrumentlist){
  print(sprintf("Transactions for the instrument: %s", instrument))
  txns <- getTxns(Portfolio = portfolioname, Symbol = instrument)
  txns.pr <- txns[,c(1,2,4,6)]
  colnames(txns.pr) <- c("Quantity","Price","Value","Net realized Profit")
  print(txns.pr)
  writeLines("")
}
```

### Step 3: Graph which visualize transactions
The following graphs show the combined view of the performance of the Smash Day trading system. It visualizes the trades (buy-transactions are visualized in green and sell-transactions are visualized in red). Moreover, the size of the blue squares indicates the size of the position (height) and the holding duration of the position (width). The green line shows the cummulative net profit curve, while the red line indicates the drawdown on each day compared to the last reached high.

```{r message=FALSE}
# Plot graph with indicators for transaction 
for (instrument in instrumentlist){
  chart.Posn(portfolioname,
             Symbol=instrument,
             type='candlesticks', 
             theme=myTheme,
             subset=daterange,
             TA=addEMAString)
}
```

### Step 4: Performance Statistics
The following table summarizes some important trading statistics for all instruments. This statistic is just an excerpt of the overall statistics which can be calculated. It is printed here as it can be assumed that they are interesting for investers to rate the trading strategy.

```{r message=FALSE}
library(PerformanceAnalytics)
# Get returns for the account
rets <- PortfReturns(Account=accountname) 
rownames(rets) <- NULL
tstats <- tradeStats(Portfolio=portfolioname, Symbols=instrumentlist)
for (i in 1:nrow(tstats)) {
  trades.tab <- cbind(
    c("Trades", "Win Percent", "Loss Percent","W/L Ratio"),
    c(tstats[i,"Num.Trades"],
      round(tstats[i,"Percent.Positive"],2),
      round(tstats[i,"Percent.Negative"],2),
      round((tstats[i,"Percent.Positive"]/tstats[i,"Percent.Negative"]),2)))
  trades1 <- trades.tab
  rownames(trades1) <- c("Trades", 
                         "Win Percent", 
                         "Loss Percent", 
                         "W/L Ratio")
  trades1 <- trades1[,2]
  print(row.names(tstats[i,]))
  print(trades1)
  writeLines("")
  }
```

### Step 5: Calculate statistics of the Portfolio and all instruments in the portfolio

```{r message=FALSE, echo=FALSE}
tab.perf <- table.Arbitrary(rets, metrics=c("Return.cumulative",
                                            "Return.annualized",
                                            "SharpeRatio.annualized",
                                            "CalmarRatio"),
                            metricsNames=c("Cumulative Return", 
                                           "Annualized Return", 
                                           "Annualized Sharp Ratio",
                                           "Calmar Ratio"))
tab.risk <- table.Arbitrary(rets, metrics=c("StdDev.annualized",
                                            "maxDrawdown",
                                            "VaR",
                                            "ES"),
                            metricsNames=c("Annualized StdDev", 
                                           "Max Drawdown",
                                           "Value-at-Risk",
                                           "Conditional VaR"),
                            method=c("historical"))
colnames(tab.perf) <- substr(colnames(tab.perf),1,3)
colnames(tab.risk) <- substr(colnames(tab.risk),1,3)

writeLines("Performance Metrics")
tab.perf
writeLines("Risk Metrics")
tab.risk
```

### Step 6: Visualize returns of the trading strategy for every instrument
The following plots visualizes some important information about the returns of the strategy applied to the instruments on the instrumentlist. The cummulative return over the entire period, the daily returns and the drawdown for each instrument is illustrated.

```{r message=FALSE, warning=FALSE, rsults="hide"}
for (i in 1:ncol(rets)){
  charts.PerformanceSummary(rets[,i],colorset=rainbow12equal,lwd=1,main=substr(colnames(rets[,i]),1,3))
}
```

### Step 7: Could we have performed better or even worse? MAE / MFE

The efficiency of a strategy is also dependent on the question whether we could have performed better or worse. This can be shown with the maximum adverse excursion and the maximum favorable excursion. The Maximum Adverse excursion shows how much we could have lost at most during the trade, while the maximum favorable excursion shows how much we could have earned more than we did. 

#### MAE

```{r message=FALSE, warning=FALSE, rsults="hide"}
for (instrument in instrumentlist){
  chart.ME(portfolioname, instrument, type="MAE", scale="percent")
}
```

#### MFE

```{r message=FALSE, warning=FALSE, rsults="hide"}
for (instrument in instrumentlist){
  chart.ME(portfolioname, instrument, type="MFE", scale="percent")
}
```

## Compare with Buy and Hold Strategy
In order to compare the trading strategy properly we need to define a benchmark against which we can measure the results. In this case a simple buy and hold strategy is used. At the first date of the trading period we place a buy order and sell our position at the last day of the selected period.
In order to do this we create a new Portfolio and a new Account. As stocks from the DAX (German Stocks Market Index) are used in the strategy, the buy and hold strategy is performed on an DAX ETF.

### Step 1: Perform the Buy and Hold Strategy

```{r message=FALSE, results="hide"}
  # Any objects, in case there was a buyhold 
  # portfolio initialized before are removed
  suppressWarnings(try(rm(list=c("account.buyhold",
                                 "portfolio.buyhold"),
                          pos=.blotter)))
  
  # The Buy and hold instrument is loaded 
  LoadCourseFile(BuyHoldDirectory,BuyHoldInstrument,debugme=TRUE,dates=daterange)
  # The Buy and hold instrument is initialized
  stock(BuyHoldInstrument,currency="EUR")
  
  BuyHoldSymbol<-get(BuyHoldInstrument)
  
  # The portfolio and account "buyhold" is initialized
  initPortf("buyhold",
            BuyHoldInstrument,
            initDate=initdate,
            currency="EUR")
  initAcct("buyhold",
           portfolios="buyhold",
           initDate=initdate,
           initEq=startCapital,
           currency="EUR")
  
  # The first date of the defined daterange is selected
  currentdate <- first(time(BuyHoldSymbol))
  
  # The close price at this date is selected
  closeprice <- as.numeric(Cl(BuyHoldSymbol[currentdate,]))
  
  # Calculate the unitsize we can buy with our startingcapital
  unitsize <- as.numeric(trunc(startCapital/closeprice))
  
  # Place the transaction for the instrument at the first date
  addTxn("buyhold",
         Symbol=BuyHoldInstrument,
         TxnDate=currentdate,
         TxnPrice=closeprice,
         TxnQty=unitsize,
         TxnFees=transactionCost)
  
  # Select the last date of the daterange period
  lastdate <-last(time(BuyHoldSymbol))
  
  # Select the price at the last date
  lastprice <- as.numeric(Cl(BuyHoldSymbol[lastdate,]))
  
  # Sell the position at the last date of the daterange
  addTxn("buyhold",
         Symbol=BuyHoldInstrument,
         TxnDate=lastdate,
         TxnPrice=lastprice,
         TxnQty=-unitsize,
         TxnFees=transactionCost)
  
  # update portfolio and account
  updatePortf(Portfolio="buyhold")
  updateAcct(name="buyhold")
  updateEndEq(Account="buyhold")
```  
  
### Step 2: Visualize the Buy and Hold strategy
We can see that we hold the position from the first until the last date. The cumulative profits are visualized by the green line.

```{r message=FALSE}
  chart.Posn("buyhold",Symbol=BuyHoldInstrument, theme=myTheme)
```

### Step 3: Compare the returns of the trading strategy with the buy and hold strategy
In order to compare the results of both strategies, we calculat the returns for the buy and hold strategy and combine them with the returns of the trading strategy which were calculated before.

```{r message=FALSE, results="hide"}
rets.bh <- PortfReturns(Account='buyhold')
returns <- cbind(rets,rets.bh)
colnames(returns) <- substr(colnames(returns),1,3)
```

In order to compare the performance between the strategy investment in one of the stocks and the alternative buy and hold strategy of the DAX ETF, the following graphs visualize the relative performance between each of the stocks used and the DAX ETF.

```{r message=FALSE}
table.Stats(returns)
table.AnnualizedReturns(returns)
# charts.PerformanceSummary(returns,geometric=FALSE,wealth.index=TRUE)
chart.RiskReturnScatter(returns,Rf=0,
                        add.sharpe=c(1,2),
                        xlim=c(0,0.35),
                        main="Return versus Risk"
                        )

for (i in colnames(returns[,-which(names(returns) == "DAX")])){
  
  print(chart.RelativePerformance(returns[,i],returns[,"DAX"],
                          colorset=c("red","blue"),
                          lwd=1,
                          legend.loc="topleft"))
}
```

## Calculations and visualizations based on returns
The visualization of returns, equity curve, value at risk and some other measure which can be calculated based on the returns of the trading strategy, can be observed in the following graphs.

### Returns and Equity Curve

```{r echo=FALSE, message=FALSE, warning=FALSE, results="hide"}
for (i in 1:length(instrumentlist)){
  # Plot the Returns of each instrument
  print(plot(rets[,i], lwd = 1, main = paste("Returns of ", substr(colnames(rets[,i]),1,3), sep="")))
  
  # Plot the equity curve of each instrument
  equityCurve <- cumprod(1 + rets[,i])
  print(plot(equityCurve, lwd = 1, main = paste("Equity curve of ", substr(colnames(rets[,i]),1,3), sep="")))
  
  # Plot the Histogram of the returns to see the return distribution and compare with a random distribution.
  set.seed(123)
  random_dist <- rnorm(length(rets[,i]),mean=mean(rets[,i]),sd=sd(rets[,i]))
  # make them into an "index-matching" time series - just for plotting
  random_dist_stats <- xts(random_dist,index(rets))
  
  random_dist_stats_density <- density(random_dist_stats)
  hist(rets[,i],probability=TRUE,breaks=100,main=paste("Histogram of Simple Returns of ",substr(colnames(rets[,i]),1,3), sep = ""), ylim = c(0,100))
  points(random_dist_stats_density,type="l")
}
```

### Value at Risk
The historical "Value at Risk" measures the risk of loss for investments. More specifically, it describes the maximum amount we would expect to lose per day with a confidencelevel of 99%, given an investment of 10000.

```{r echo=FALSE, message=FALSE, warning=FALSE}

Investment <- 10000
probs <- 0.01
print(sprintf("Investment: %s", Investment))
writeLines("")
print(sprintf("Confidence Level: %s", (1-probs)))
writeLines("")
      
for (i in 1:length(instrumentlist)) {
  quantile(rets[,i])
  (discreteRQ <- quantile(rets[,i],probs=probs))
  loss <- Investment * discreteRQ
  print(sprintf("Given a %s investment in %s we would expect a maximum loss of %s per day.", Investment, substr(colnames(rets[,i]),1,3), round(loss,2)*-1))
}
```

# Conclusion and Suggestions
